Interval-Valued Quantum Probabilities: Contextuality and the Born Rule

### 2017-07-06 prop_letter.tex
prop_letter.tex Trim Reference...

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Artstein1972,Shafer1976,GilboaSchmeidler1994,Marinacci1999,Weichselberger2000,JamisonLodwick2004,Galvan2008,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition. For
general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Marinacci1999,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199,Jaeger2007}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

@@

The expectation value is intuitively between two possible outcomes
which lie between the minimum and maximum bounds of the given
probability intervals. (This definition is consistent with the
classical Choquet integral on commuting sub-event spaces by adopting
the classical
results\nb\cite{Rosenmuller1971,GilboaSchmeidler1994,Grabisch2016}.)
If the QIVPM is cryptodeterministic, this interval collapses to a
singleton $\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
of~$\mathbf{O}$. If we define the multiplication of two singleton
sets\nb$\left\{ \lambda_{1}\right\} $ and
$\left\{ \lambda_{2}\right\} $ to be
$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.

>>>>

We will start by reviewing IVPMs in the classical setting and then
propose our quantum generalization. In the classical setting, there
are several proposals for ``imprecise
probabilities''~\citep{Dempster1967,Shafer1976,GilboaSchmeidler1994,Weichselberger2000,JamisonLodwick2004,HuberRonchetti2009,Grabisch2016}.
Although these proposals differ in some details, they all share the
fact that the probability $\mu(E)$ of an event~$E$ is generalized from
a single real number to an interval of certainty $[\ell,r]$
where\nb$\ell$ intuitively corresponds to the strength of evidence for
the event and~$r$ corresponds to the strength of evidence against the
event. The collection of intervals used in the definition of a
probability measure must satisfy certain properties which we explain
next.

@@

When combining non-disjoint events, there is a further subtlety whose
resolution will give the most general and final condition. For
general, non-necessarily disjoint events $E_1$ and $E_2$, we have:
\begin{equation}
\mu(E_1\cup E_2) + \mu(E_1\cap E_2) \subseteq \mu(E_1) + \mu(E_2)
\label{eq:classicalconvex}
\end{equation}
which is a generalization of the classical inclusion-exclusion
principle that uses $\subseteq$ instead of $=$ for the same reason as
before. The new condition, known as
\emph{convexity}\nb\cite{Shapley1971,GilboaSchmeidler1994,Grabisch2016},
reduces to the previously
motivated condition when the events are disjoint, i.e., when
$\mu(E_1\cap E_2) = 0$.

@@

Contrary to the case with conventional quantum probability spaces,
there is generally no unique state consistent with a QIVPM. Given
observations done with finite resources, the probabilities become
intervals, and we say a state\nb$\rho$ is consistent with $\bar{\mu}$ on
a projector\nb$P$ if
$\mu_{\rho}^{\mathrm{B}}\left(P\right)\in\bar{\mu}\left(P\right)$, and
denoted by
$\rho\in\coreBorn\left(\bar{\mu},\left\{ P\right\} \right)$,
where $\mu_{\rho}^{\mathrm{B}}\left(P\right)=\Tr\left(\rho P\right)$
is the probability that the event\nb$P$ happens determined by the
Born rule\nb\cite{Born1983,peres1995quantum,544199}.
Moreover, $\rho\in\coreBorn\left(\bar{\mu},S\right)$ means~$\rho$ is
consistent with $\bar{\mu}$ on every projector in $S$.

@@

The expectation value is intuitively between two possible outcomes
which lie between the minimum and maximum bounds of the given
probability intervals. (This definition is consistent with the
classical Choquet integral on commuting sub-event spaces by adopting
the classical
results\nb\cite{GilboaSchmeidler1994,Grabisch2016}.)
If the QIVPM is cryptodeterministic, this interval collapses to a
singleton $\left\{ \lambda\right\} $, where $\lambda$ is an eigenvalue
of~$\mathbf{O}$. If we define the multiplication of two singleton
sets\nb$\left\{ \lambda_{1}\right\} $ and
$\left\{ \lambda_{2}\right\} $ to be
$\left\{ \lambda_{1}\lambda_{2}\right\} $, then we have
\begin{equation}
\prod_{j=1}^{N}\expval{\mathbf{O}_{j}}_{\bar{\mu}}=\expval{\prod_{j=1}^{N}\mathbf{O}_{j}}_{\bar{\mu}}\label{eq:Kochen-Specker-Rules}
\end{equation}
for any sequence of commuting observables\nb$\left\{ \mathbf{O}_{j}\right\} _{j=1}^{N}$.
